Formalizing Stack Safety as a Security Property

### 2022-09-05 submission5/onlyformalism.tex

The labeled step function for overlay states
\(\sigma \stepstounder{\psi?} \sigma' \in
\mathcal{S} \rightarrow  (\Psi + \bot) \times \mathcal{S}\)
proceeds by an {\it overlay step}
if the program counter points to the start of a macro-instruction's instruction sequence.
Otherwise, it proceeds by the default step. The definitions of context steps
\(\constep{\psi} \in \CONTEXTS \times \Psi \rightarrow \CONTEXTS\)
will be defined for each pseudoinstruction as we introduce new topics.

\judgmentthreebrlong[Overlay]
                    {\((\bar{i}, \psi) \in J\)}
                    {\(\mach',\context \constep{\psi} \context'\)}
                    {\(\mach \manystepstounder{} \mach'\)}
                    {\(\mach[\PCname+n] = \bar{i}[n]\) for each \(n\) where \(0 \leq n < |\bar{i}|\)}
                    {\((\mach,\context)) \stepstounder{\psi} (\mach',\context')\)}

@@

\begin{figure*}
\[\begin{split}
& \mathit{update\_view} ~ V ~ a_{sp} ~ \overline{r_{args}} \triangleq
\lambda \component .
\begin{cases}
  \public & \textnormal{else if } \component \in \REGS \textnormal{ and }
  \component \in \overline{r_{args}} \textnormal{ or } \component \in \mathit{PUBLIC} \\
  \unsealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } \component \leq a_{sp} \\
  \sealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } a_{sp} < \component \textnormal { and } V ~ \component = \unsealed \\
  V ~ \component & \textnormal{otherwise} \\
\end{cases} \\
\end{split}\]

@@

\definition An element set \(\components\) is vestigial in state \(\sigma)\),
written \((\mach,\context) \parallel \components\), if for all
\(\nach\) such that \(\mach \approx_{\components'} \mach'\), if 
\((\mach,\context) \hookrightarrow \obsT\) and
\((\nach,\context) \hookrightarrow \obsT'\), then
\(\obsT \eqsim \obsT'\).

@@

Then \((\mach,\context)\) enjoys {\it caller confidentiality} with respect to
some \(\context_{ret}\) if, for any \(\nach\)
that is a \(\components\)-variant of \(\mach\), we can take
\(\context \uparrow (\mach,\context) \hookrightarrow \obsT\) and
\(\context \uparrow (\nach,\context) \hookrightarrow \obsT'\) and have that
\(\obsT \simeq \obsT'\);
and additionally if \((\mach,\context) ~ (\context_{ret} \Uparrow R) ~ (\nach,\context)\),
where \((\mach_1,\context_1) ~ R ~ (\nach_2,\context_2)\) if
\((\mach_1 \parallel \bar{\Diamond}(\mach,\mach_1,\nach,\nach_2)\).

>>>>

The labeled step function for overlay states
\(\sigma \stepstounder{\psi?} \sigma' \in
\mathcal{S} \rightarrow  (\Psi + \bot) \times \mathcal{S}\)
proceeds by an {\it overlay step}
if the program counter points to the start of a macro-instruction's instruction sequence.
Otherwise, it proceeds by the default step. The definitions of context steps
\(\constep{\psi} \in \MACHS \times \CONTEXTS \times \Psi \rightarrow \CONTEXTS\)
will be defined for each pseudoinstruction as we introduce new topics.

\judgmentthreebrlong[Overlay]
                    {\((\bar{i}, \psi) \in J\)}
                    {\(\mach',\context \constep{\psi} \context'\)}
                    {\(\mach \manystepstounder{} \mach'\)}
                    {\(\mach[\PCname+n] = \bar{i}[n]\) for each \(n\) where \(0 \leq n < |\bar{i}|\)}
                    {\((\mach,\context) \stepstounder{\psi} (\mach',\context')\)}

@@

\begin{figure*}
\[\begin{split}
& \mathit{update\_view} ~ V ~ a_{sp} ~ \overline{r_{args}} \triangleq
\lambda \component .
\begin{cases}
  \public & \textnormal{else if } \component \in \REGS \textnormal{ and }
  \component \in \overline{r_{args}} \textnormal{ or } \component \in \mathit{PUBLIC} \\
  \unsealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } \component \leq a_{sp} \\
  \unsealed & \textnormal{else if } \component \in \REGS \textnormal{ and } \component \in \mathit{CLR\_SV} \\
  \sealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } a_{sp} < \component \textnormal { and } V ~ \component = \unsealed \\
  \sealed & \textnormal{else if } \component \in \REGS  \\
  V ~ \component & \textnormal{otherwise} \\
\end{cases} \\
\end{split}\]

@@

\definition An element set \(\components\) is vestigial in state \((\mach,\context)\),
written \((\mach,\context) \parallel \components\), if for all
\(\nach\) such that \(\mach \approx_{\components'} \mach'\), if 
\((\mach,\context) \hookrightarrow \obsT\) and
\((\nach,\context) \hookrightarrow \obsT'\), then
\(\obsT \eqsim \obsT'\).

@@

Then \((\mach,\context)\) enjoys {\it caller confidentiality} with respect to
some \(\context_{ret}\) if, for any \(\nach\)
that is a \(\components\)-variant of \(\mach\), we can take
\(\context_{ret} \uparrow (\mach,\context) \hookrightarrow \obsT\) and
\(\context_{ret} \uparrow (\nach,\context) \hookrightarrow \obsT'\) and have that
\(\obsT \simeq \obsT'\);
and additionally if \((\mach,\context) ~ (\context_{ret} \Uparrow R) ~ (\nach,\context)\),
where \((\mach_1,\context_1) ~ R ~ (\nach_2,\context_2)\) if
\((\mach_1 \parallel \bar{\Diamond}(\mach,\mach_1,\nach,\nach_2)\).
